---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Study Messages {.unnumbered}

```{r}
library(tidyverse)
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/print_kbl.R?raw=true")
```

Coco Yu

Last updated: 10/6/2023

## Communications collection procedure

Participants completed a semi-structured interview at intake and each of the three follow-up visits over the course of three months that collects information about frequently communicated contacts. Interview questions include contextual information about each contact was used to get drinking (e.g., past-drinking history with a contact) and risk-related information (e.g., pleasantness or unpleasantness of interacting with a contact).

At intake, participants reported contact communications retrospectively. At each one-month follow-up visit, the researchers directly backed up the participants' non-deleted text messages and phone call logs from phone. Contextual questions about newly identified people were asked.

## Data Files

| Data type                         | Level      | Location                                             |
|---------------------|------------------|---------------------------------|
| Raw Contact Information           | Individual | studydata/risk/data_raw/###/###\_Contacts.xlsx       |
| Raw SMS Messages on IOS           | Individual | studydata/risk/data_raw/###/###\_SMS\_#.sql          |
| Raw SMS Messages on Android       | Individual | studydata/risk/data_raw/###/###\_SMS\_#.xml          |
| Processed Contact Information     | Individual | studydata/risk/data_processed/shared/contacts.csv    |
| Processed SMS Messages on Android | Individual | studydata/risk/data_processed/shared/sms_android.csv |
| Processed SMS Messages on IOS     | Individual | studydata/risk/data_processed/shared/sms_ios.csv     |

## Data processing

### Data cleaning and concatenating

| Name                | Path                                                 | Function                                                      | Input                                          | Output          |
|---------------|---------------|---------------|---------------|---------------|
| cln_contacts.rmd    | analysis_risk/shared/scripts_cln/cln_contacts.rmd    | cleans up contact information for EDA                         | individual contact files (###\_Contacts.xlsx)  | contacts.csv    |
| cln_sms_android.rmd | analysis_risk/shared/scripts_cln/cln_sms_android.rmd | cleans up text messages information on android device for EDA | up to three text message for each participant  | ###\_SMS\_#.xml |
| cln_sms_ios.rmd     | analysis_risk/shared/scripts_cln/cln_sms_ios.rmd     | cleans up text messages information on ios device for EDA     | up to three text messages for each participant | ###\_SMS\_#.sql |


## Data Dictionaries

```{r}
d <- read_csv("tmp.csv")

d |> print_kbl()
```

